Workflow for Ecov Recruitment Analysis

### 2024-01-23 Ecov_study/recruitment_functions/Workflow_Ecov_Recruitment_Project.Rmd
bias_parameters.R complete
includes plots, regression tree, 1 table; Rmd workflow updated

5. Look at bias in parameter estimates **bias_parameters.R**
   + SR_a, SR_b, sigmaR, rho_R, sigmaEcov, rho_Ecov
   + also grabbing catchability (logit_q), selectivity (logit_selpars), catch_paa_pars, and index_paa_pars parameters so i don't have to pass through results again
   + Runtime ...pending
   + **<span style="color: blue;">STATUS: pending beta unstandardized; </span>**

>>>>

5. Look at bias in parameter estimates **bias_parameters.R**
   + specify gradient and SE tolerance at top (these were appended to AIC dataframe outputs in the step above)
   + specify results directory (where runs are), directory where to save plots, and a suffix to append at end of file name (to distinguish plots for different cases)
   + SR_a, SR_b, sigmaR, rho_R, sigmaEcov, rho_Ecov
   + also grabbing catchability (logit_q), selectivity (logit_selpars), catch_paa_pars, and index_paa_pars parameters so i don't have to pass through results again
   + all Truth values also grabbed, RE calculated and plotted based on factors from regression trees
   + Runtime 1.17 hours
   + **<span style="color: blue;">STATUS: done beta unstandardized; </span>**

5. Cleaning up script **compare_projections.R**
   + this calculates mohn's rho for user-specified number of peels, evaluates relative error from peel 10 to peel 0, ...
   + Runtime ...
   + **<span style="color: blue;">STATUS: pending... beta unstandardized; </span>**
